\begin{center}
    \large \textbf{Abstract}\\

    \medskip

    \large Fire Weather Testbed Evaluation of SmokeViz: A Deep Learning Wildfire Smoke Plume Analysis Product for Data Assimilation 
\end{center}

\bigskip

\noindent\textbf{Project Goal:} In order to address the need to advance predictive capabilities for wildfire smoke dispersion and air quality, we present an innovative and computationally efficient smoke analysis product, SmokeViz. 

\bigskip

\noindent\textbf{Problem/Opportunity Statement:} Currently, wildfire smoke plume models such as HRRR and RRFS have a significant latency for representing the plumes from recently started wildfires. This project addresses the operational need to address model latency for wildfire smoke by providing a timely and reliable smoke observation product for data assimilation into air quality prediction models. 

\bigskip

\noindent\textbf{Methodology and Timeline:} Over the proposed two year timeline, we will validate SmokeViz’s capabilities to identify smoke over North America. Then we will integrate and evaluate SmokeViz as input to HRRR-Smoke as a data assimilation product within an operational context.

\bigskip

\noindent\textbf{Primary Project Products/Outputs:} The project will produce an operationally-ready smoke analysis product that can be used for near-realtime data assimilation for air quality models. 

\bigskip

\noindent\textbf{Expected Results, Outcomes, and Benefits:} The expected result will be a deep learning based smoke analysis product that describes the current extent and categorical density of smoke. Used as a smoke data assimilation product, SmokeViz is expected to significantly advance short-range model predictive capabilities for rapidly evolving wildfires.

\bigskip

\noindent\textbf{Intended Beneficiaries and Recipients:} Expected end-users SmokeViz would include HMS analysts and scientists that create and run the air quality and smoke plume dispersion models along with down-the-line air quality forecasters and decision makers.

\bigskip

\noindent\textbf{Readiness Levels:} The current RL for this project is RL 5 where we have performed evaluation and testing for SmokeViz on streaming GOES imagery. At the end of this project timeline, we will work with a transition partner to reach readiness level 8.


